Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2020-12-31 PaperVictor.tex
Revise theory

%\title{Thickness optimization in wide range quasi omnidirectional multilayer
% structures}
\title{ Thickness optimization in wide range quasi
omnidirectional 1-D photonic structures}
\author[1,2,3]{Victor Castillo-Gallardo\thanks{email: {\tt
			victor1\_1@hotmail.com}}}
\author[1,2,3]{Luis Eduardo Puente-D\'{i}az}
\author[4]{D. Ariza-Flores}
\author[3]{Hector P\'{e}rez-Aguilar}
\author[2]{W. Luis Moch\'{a}n\thanks{email: {\tt
			mochan@fis.unam.mx}}}
\author[1]{Vivechana Agarwal\thanks{email: {\tt
			vagarwal@uaem.mx}}}
\affil[1]{Centro de Investigaci\'{o}n en Ingenier\'{i}a y
Ciencias Aplicadas, Universidad del Estado de Morelos, Av.
Universidad 1001, Col. Chamilpa, Cuernavaca, Morelos 62209,
M\'{e}xico.}
\affil[2]{Instituto de Ciencias F\'{i}sicas, Universidad
Nacional Aut\'{o}noma de M\'{e}xico, Av. Universidad S/N,
Col. Chamilpa, 62210 Cuernavaca, Morelos, México.}
\affil[3]{Facultad de Ciencias Fìsico Matem\'{a}ticas,
Universidad Michoacana de San Nicol\'{a}s de Hidalgo, Av.
Francisco J. Múgica S/N 58030, Morelia, Mich., M\'{e}xico.}
\affil[4]{CONACyT-Universidad Aut\'{o}noma de San Luis
Potosì, Karakorum 1470, Lomas 4ta Secc, San Luis Potos\'{i},
S.L.P., 78210, M\'{e}xico.}
%\date{{\small {\today}}}
\maketitle

@@

\section{Theoretical analysis}\label{s:theory}

\notaL{Pon etiquetas a todo para poderlo referir}
In the analysis of the propagation of the electromagnetic field through
multilayer systems, it is common to employ the transfer matrix method (put the
reference). Under the consideration that the system only varies along the $z$ axis, the
transfer matrix is $M\left(z_{2},z_{1}\right)$
a 2x2 matrix that relates the components of the electric field E$_{\parallel }$
and the magnetic field H$_{\parallel }$ parallel to the $xy$ plane, and
normal to the axis of the structure, evaluated at any two points $z_{2}$
and $z_{1}$
\begin{equation*}
\left(
\begin{array}{c}
E_{\Vert } \\
H_{\Vert }%
\end{array}%
\right) _{z_{2}}=M\left( z_{2},z_{1}\right) \left(
\begin{array}{c}
E_{\Vert } \\
H_{\Vert }%
\end{array}%
\right) _{z_{1}}.
\end{equation*}%
Many equivalent formulations have been proposed to obtain $M$
\cite{Mochan1987,Ortiz2020,Chavez2020}. Here we use a recently developed formalism
to calculate the reflectance of large multilayer systems proposed by Puente-D%
\'{\i}az, et al. \cite{Puente2020}, since we need a reliable and stable tool
to design an optimized structure through a minimization procedure that
requires the calculation of complete spectra for all sets of design parameters.
The development of $M$ is shown in the supplementary information. Therefore, the
explicit expressions for the optical coefficients are:
\begin{equation}
r=\mp \frac{Z_{0}\tilde{M}_{11}+\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}_{21}-Z_{s}%
\tilde{M}_{22}}{Z_{0}\tilde{M}_{11}-\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}%
_{21}+Z_{s}\tilde{M}_{22}},  \label{rBloch}
\end{equation}%
and
\begin{equation}
t=\frac{2Z_{\alpha }}{Z_{0}\tilde{M}_{11}-\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}%
_{21}+Z_{s}\tilde{M}_{22}},  \label{tBloch}
\end{equation}%
where the upper sign $-$ in Eq. (\ref{rBloch}) and the subscript $\alpha =s$
in Eq. (\ref{tBloch}) are chosen for the case of TE polarization, while
the lower sign $+$ and the subscript $\alpha =0$ correspond to TM
polarization, respectively. Furthermore, $\tilde{M}_{ij}$ are the elements of the transfer matrix. As usual, the reflectance is given by $R=|r|^{2}$ and the
transmittance by $T=\beta \left\vert t\right\vert ^{2}$ with $\beta
=Z_{0}/Z_{s}$ for the case of TE polarization and $\beta =Z_{s}/Z_{0}$ for
the case of TM polarization. Additionally, complex refractive indices of the porous
layers in the simulations were obtained by Bruggeman effective medium theory, which
has been reported to adequately reproduce the PS optical parameters
\cite{Giusseppe2011,Pap2006,Estrada2018}.

After the next section, two techniques are developed to design multilayer
photonic structures. In the first, the wavelength ($\lambda _{j}$), at which
the $j$-th period of the structure is designed, is modulated by an
increasing function. This can be as simple or complex as you like. The
proposed function was optimized with the Minuit module of PDL (Perl Data
Language) \cite{minuit}. The other technique for proposing highly reflective
structures over a wide region of the electromagnetic spectrum is to stack
sub-mirrors tuned to different wavelengths. For each sub-mirror the
dispersion relation is analyzed.

>>>>

%\title{Thickness optimization in wide range quasi omnidirectional multilayer
% structures}
\title{Optimization of wide-band quasi-omnidirectional 1-D photonic structures}
\author[1,2,3]{Victor Castillo-Gallardo\thanks{email: {\tt
			victor1\_1@hotmail.com}}}
\author[1,2,3]{Luis Eduardo Puente-D\'{i}az}
\author[4]{D. Ariza-Flores}
\author[3]{Hector P\'{e}rez-Aguilar}
\author[2]{W. Luis Moch\'{a}n\thanks{email: {\tt
			mochan@fis.unam.mx}}}
\author[1]{Vivechana Agarwal\thanks{email: {\tt
			vagarwal@uaem.mx}}}
\affil[1]{Centro de Investigaci\'{o}n en Ingenier\'{i}a y
Ciencias Aplicadas, Universidad del Estado de Morelos, Av.
Universidad 1001, Col. Chamilpa, Cuernavaca, Morelos 62209,
M\'{e}xico.}
\affil[2]{Instituto de Ciencias F\'{i}sicas, Universidad
Nacional Aut\'{o}noma de M\'{e}xico, Av. Universidad S/N,
Col. Chamilpa, 62210 Cuernavaca, Morelos, México.}
\affil[3]{Facultad de Ciencias Fìsico Matem\'{a}ticas,
Universidad Michoacana de San Nicol\'{a}s de Hidalgo, Av.
Francisco J. Múgica S/N 58030, Morelia, Mich., M\'{e}xico.}
\affil[4]{CONACyT-Universidad Aut\'{o}noma de San Luis
Potosì, Karakorum 1470, Lomas 4ta Secc, San Luis Potos\'{i},
S.L.P., 78210, M\'{e}xico.}
%\date{{\small {\today}}}
\maketitle

@@

\section{Theory}\label{s:theory}

\notaL{Pon etiquetas a todo para poderlo referir}
For the analysis of the propagation of electromagnetic fields through
multilayer systems it is usual to employ the transfer matrix
method\notaL{reference}. Assuming the system is 1D, with variations
only along the $z$ directions, and that the polarization of light is either
transverse electric (TE) or transverse magnetic (TM)\notaL{si no, la matriz
  sería de 4x4}, the
transfer matrix $M\left(z_{2},z_{1}\right)$ is
a 2x2 matrix that relates the components of the electric $E_{\| }$
and magnetic  $H_{\|}$ fields parallel to the $xy$ plane
evaluated at $z_2$ to their value at $z_{1}$,
\begin{equation*}
\left(
\begin{array}{c}
E_{\|} \\
H_{\| }%
\end{array}%
\right) _{z_{2}}=M\left( z_{2},z_{1}\right) \left(
\begin{array}{c}
E_{\| } \\
H_{\| }%
\end{array}%
\right) _{z_{1}}.
\end{equation*}%
Many equivalent formulations have been proposed to obtain and use $M$
\cite{Mochan1987,Ortiz2020,Chavez2020}. Here we use a recently developed formalism
for the numerically stable calculation of the reflectance of large
multilayer systems, as
proposed by Puente-Díaaz, et al. \cite{Puente2020}, summarized in the
supplementary information. The
explicit expressions for the optical coefficients are:
\begin{equation}
r=\mp \frac{Z_{0}M_{11}+M_{12}-Z_{0}Z_{s}M_{21}-Z_s
M_{22}}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{rBloch}
\end{equation}%
and
\begin{equation}
t=\frac{2Z_{\alpha
  }}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{tBloch}
\end{equation}%
where $M_{ij}$ \notaL{Quité las tildes, pues hubiera sido necesario
  explicarlas, y no creo que sean importantes para el lector} are the elements
of the transfer matrix which transfer
the fields from its surface interface with vacuum at $z_0$ towards the
substrate at $z_s$,  $Z_0$ is the surface impedance of vacuum and $Z_s$ is the
surface impedance of the substrate, and we define $r=F_r/F_i$ and $t=F_t/F_i$ in terms
of the reflected and transmitted fields, where we choose the $F$'s as electric
fields for (TE) polarization and magnetic fields
for transverse magnetic polarization (TM). The upper sign $-$ in
Eq. (\ref{rBloch}) and the subscript $\alpha =s$
in Eq. (\ref{tBloch}) are chosen for the case of TE polarization, while
the lower sign $+$ and the subscript $\alpha =0$ correspond to TM
polarization, respectively.
The reflectance is given by
$R=|r|^{2}$ and the
transmittance by $T=\beta \left\vert t\right\vert ^{2}$ with $\beta
=\text{Re}Z_{0}/\text{Re}Z_{s}$ for TE polarization and $\beta =\text{Re}Z_{s}/\text{Re}Z_{0}$ for
TM polarization.\notaL{En el cálculo, ¿tomaste las partes reales? No
  estaban en la fórmula} The complex refractive index of the porous
layers were obtained through the Bruggeman's effective medium theory, which
has been reported to adequately reproduce the PS optical parameters
\cite{Giusseppe2011,Pap2006,Estrada2018}.

\notaL{Creo que esto debería estar más adelante:
  After the next section, two techniques are developed to design multilayer
photonic structures. In the first, the wavelength ($\lambda _{j}$), at which
the $j$-th period of the structure is designed, is modulated by an
increasing function. This can be as simple or complex as you like. The
proposed function was optimized with the Minuit module of PDL (Perl Data
Language) \cite{minuit}. The other technique for proposing highly reflective
structures over a wide region of the electromagnetic spectrum is to stack
sub-mirrors tuned to different wavelengths. For each sub-mirror the
dispersion relation is analyzed.
}
